A comparison of design-based and model-based approaches for finite population spatial data -- Supplementary Material.

### 2021-12-18 inst/manuscript/supplementary.tex
minor updates
reanalyzing simulation data
minor manuscript updates
update to remove figures and application computations from main body of text

  \journal{An awesome journal} % Sets Journal name

@@

  \title{A comparison of design-based and model-based approaches for finite
population spatial data -- Supplementary Material.}
    \author[USEPA]{Michael Dumelle\corref{1}}
   \ead{Dumelle.Michael@epa.gov} 
    \author[STLAW]{Matt Higham}
   \ead{mhigham@stlaw.edu} 
    \author[OSU]{Lisa Madsen}

@@

      \address[USEPA]{United States Environmental Protection Agency, 200 SW 35th St,
Corvallis, Oregon, 97333}
    \address[STLAW]{Saint Lawrence University Department of Mathematics, Computer Science,
and Statistics, 23 Romoda Drive, Canton, New York, 13617}
    \address[OSU]{Oregon State University Department of Statistics, 239 Weniger Hall,
Corvallis, Oregon, 97331}
    \address[NOAA]{Marine Mammal Laboratory, Alaska Fisheries Science Center, National
Oceanic and Atmospheric Administration, Seattle, Washington, 98115}
      \cortext[1]{Corresponding Author}

@@

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2 so that the partial sill was 0, 1, or 1.8.} 
\end{table}

@@

@@

IRS-Design & Gridded & Normal & 0 & 50 & -0.0001 & 0.1939 & 0.9475 \\ 
  IRS-Model & Gridded & Normal & 0 & 50 & -0.0001 & 0.1960 & 0.9370 \\ 
  GRTS-Design & Gridded & Normal & 0 & 50 & -0.0010 & 0.1930 & 0.9175 \\ 
  GRTS-Model & Gridded & Normal & 0 & 50 & -0.0016 & 0.1936 & 0.9405 \\ 

@@

@@

IRS-Design & Gridded & Lognormal & 0 & 50 & 0.0077 & 1.0498 & 0.8355 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 50 & -0.0274 & 1.2011 & 0.8230 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 50 & 0.0092 & 0.9618 & 0.7910 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 50 & -0.0069 & 0.9808 & 0.8100 \\ 

@@

IRS-Design & Random & Normal & 0 & 50 & 0.0045 & 0.1948 & 0.9410 \\ 
  IRS-Model & Random & Normal & 0 & 50 & 0.0048 & 0.1966 & 0.9360 \\ 
  GRTS-Design & Random & Normal & 0 & 50 & 0.0056 & 0.1943 & 0.9000 \\ 
  GRTS-Model & Random & Normal & 0 & 50 & 0.0057 & 0.1947 & 0.9365 \\ 

@@

IRS-Design & Random & Lognormal & 0 & 50 & 0.0116 & 0.9684 & 0.8205 \\ 
  IRS-Model & Random & Lognormal & 0 & 50 & -0.0235 & 1.0055 & 0.8150 \\ 
  GRTS-Design & Random & Lognormal & 0 & 50 & -0.0005 & 0.9151 & 0.8075 \\ 
  GRTS-Model & Random & Lognormal & 0 & 50 & -0.0175 & 0.9426 & 0.8240 \\ 

@@

IRS-Design & Gridded & Normal & 0.5 & 50 & -0.0006 & 0.1571 & 0.9600 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 50 & -0.0005 & 0.1509 & 0.9435 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 50 & 0.0006 & 0.1463 & 0.9240 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 50 & 0.0006 & 0.1443 & 0.9445 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0154 & 0.8578 & 0.8700 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0209 & 0.9091 & 0.8490 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 50 & -0.0046 & 0.8302 & 0.8400 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0167 & 0.8301 & 0.8495 \\ 

@@

IRS-Design & Random & Normal & 0.5 & 50 & 0.0089 & 0.1720 & 0.9385 \\ 
  IRS-Model & Random & Normal & 0.5 & 50 & 0.0074 & 0.1580 & 0.9310 \\ 
  GRTS-Design & Random & Normal & 0.5 & 50 & 0.0060 & 0.1460 & 0.9145 \\ 
  GRTS-Model & Random & Normal & 0.5 & 50 & 0.0059 & 0.1439 & 0.9365 \\ 

@@

IRS-Design & Random & Lognormal & 0.5 & 50 & 0.0006 & 0.8479 & 0.8670 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 50 & -0.0447 & 0.8845 & 0.8485 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 50 & 0.0022 & 0.8663 & 0.8230 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 50 & -0.0044 & 0.8620 & 0.8470 \\ 

@@

IRS-Design & Gridded & Normal & 0.9 & 50 & -0.0021 & 0.1185 & 0.9790 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 50 & -0.0023 & 0.0925 & 0.9475 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 50 & -0.0004 & 0.0957 & 0.9280 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 50 & 0.0015 & 0.0874 & 0.9300 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0191 & 0.6345 & 0.9310 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 50 & 0.0043 & 0.6031 & 0.8850 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 50 & -0.0072 & 0.6496 & 0.8890 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0144 & 0.5873 & 0.8890 \\ 

@@

IRS-Design & Random & Normal & 0.9 & 50 & -0.0022 & 0.1451 & 0.9445 \\ 
  IRS-Model & Random & Normal & 0.9 & 50 & -0.0016 & 0.1018 & 0.9350 \\ 
  GRTS-Design & Random & Normal & 0.9 & 50 & -0.0022 & 0.0963 & 0.9235 \\ 
  GRTS-Model & Random & Normal & 0.9 & 50 & -0.0016 & 0.0881 & 0.9360 \\ 

@@

IRS-Design & Random & Lognormal & 0.9 & 50 & -0.0279 & 0.7417 & 0.9080 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 50 & -0.0479 & 0.6787 & 0.8720 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 50 & -0.0101 & 0.5712 & 0.8995 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 50 & -0.0079 & 0.5143 & 0.8935 \\ 

@@

IRS-Design & Gridded & Normal & 0 & 100 & -0.0031 & 0.1343 & 0.9430 \\ 
  IRS-Model & Gridded & Normal & 0 & 100 & -0.0035 & 0.1349 & 0.9405 \\ 
  GRTS-Design & Gridded & Normal & 0 & 100 & 0.0016 & 0.1327 & 0.9200 \\ 
  GRTS-Model & Gridded & Normal & 0 & 100 & 0.0015 & 0.1327 & 0.9395 \\ 

@@

IRS-Design & Gridded & Lognormal & 0 & 100 & 0.0123 & 0.6517 & 0.8595 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 100 & 0.0037 & 0.6698 & 0.8540 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 100 & 0.0175 & 0.6309 & 0.8275 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 100 & 0.0108 & 0.6450 & 0.8460 \\ 

@@

IRS-Design & Random & Normal & 0 & 100 & 0.0058 & 0.1363 & 0.9350 \\ 
  IRS-Model & Random & Normal & 0 & 100 & 0.0062 & 0.1373 & 0.9315 \\ 
  GRTS-Design & Random & Normal & 0 & 100 & 0.0033 & 0.1351 & 0.9175 \\ 
  GRTS-Model & Random & Normal & 0 & 100 & 0.0033 & 0.1350 & 0.9460 \\ 

@@

IRS-Design & Random & Lognormal & 0 & 100 & -0.0187 & 0.6427 & 0.8595 \\ 
  IRS-Model & Random & Lognormal & 0 & 100 & -0.0394 & 0.6726 & 0.8565 \\ 
  GRTS-Design & Random & Lognormal & 0 & 100 & 0.0049 & 0.6366 & 0.8445 \\ 
  GRTS-Model & Random & Lognormal & 0 & 100 & 0.0011 & 0.6431 & 0.8585 \\ 

@@

IRS-Design & Gridded & Normal & 0.5 & 100 & -0.0005 & 0.1070 & 0.9640 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 100 & -0.0006 & 0.1041 & 0.9335 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 100 & -0.0010 & 0.1014 & 0.9145 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 100 & -0.0011 & 0.1006 & 0.9365 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 100 & 0.0156 & 0.5285 & 0.9060 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 100 & 0.0020 & 0.5346 & 0.8800 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 100 & 0.0061 & 0.4945 & 0.8595 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 100 & 0.0015 & 0.4965 & 0.8705 \\ 

@@

IRS-Design & Random & Normal & 0.5 & 100 & 0.0002 & 0.1169 & 0.9440 \\ 
  IRS-Model & Random & Normal & 0.5 & 100 & 0.0023 & 0.1042 & 0.9450 \\ 
  GRTS-Design & Random & Normal & 0.5 & 100 & 0.0030 & 0.1032 & 0.9140 \\ 
  GRTS-Model & Random & Normal & 0.5 & 100 & 0.0024 & 0.1022 & 0.9335 \\ 

@@

IRS-Design & Random & Lognormal & 0.5 & 100 & -0.0020 & 0.5609 & 0.8895 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 100 & -0.0209 & 0.5570 & 0.8835 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 100 & -0.0106 & 0.5261 & 0.8800 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 100 & -0.0199 & 0.5358 & 0.8875 \\ 

@@

IRS-Design & Gridded & Normal & 0.9 & 100 & 0.0008 & 0.0702 & 0.9915 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 100 & 0.0016 & 0.0573 & 0.9510 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 100 & 0.0002 & 0.0600 & 0.9315 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 100 & -0.0001 & 0.0540 & 0.9515 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 100 & 0.0165 & 0.4844 & 0.9595 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 100 & 0.0062 & 0.4274 & 0.8975 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 100 & 0.0056 & 0.3959 & 0.9135 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 100 & -0.0015 & 0.3764 & 0.9200 \\ 

@@

IRS-Design & Random & Normal & 0.9 & 100 & -0.0034 & 0.1021 & 0.9425 \\ 
  IRS-Model & Random & Normal & 0.9 & 100 & -0.0015 & 0.0611 & 0.9480 \\ 
  GRTS-Design & Random & Normal & 0.9 & 100 & -0.0009 & 0.0614 & 0.9275 \\ 
  GRTS-Model & Random & Normal & 0.9 & 100 & -0.0004 & 0.0548 & 0.9410 \\ 

@@

IRS-Design & Random & Lognormal & 0.9 & 100 & -0.0048 & 0.5829 & 0.9275 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 100 & -0.0287 & 0.5423 & 0.9205 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 100 & 0.0010 & 0.4351 & 0.9180 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 100 & -0.0025 & 0.3975 & 0.9140 \\ 

@@

IRS-Design & Gridded & Normal & 0 & 200 & 0.0005 & 0.0882 & 0.9455 \\ 
  IRS-Model & Gridded & Normal & 0 & 200 & 0.0005 & 0.0882 & 0.9435 \\ 
  GRTS-Design & Gridded & Normal & 0 & 200 & 0.0034 & 0.0882 & 0.9430 \\ 
  GRTS-Model & Gridded & Normal & 0 & 200 & 0.0034 & 0.0882 & 0.9500 \\ 

@@

IRS-Design & Gridded & Lognormal & 0 & 200 & 0.0109 & 0.4122 & 0.8815 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 200 & 0.0102 & 0.4128 & 0.8790 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 200 & -0.0128 & 0.4355 & 0.8825 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 200 & -0.0132 & 0.4362 & 0.8865 \\ 

@@

IRS-Design & Random & Normal & 0 & 200 & -0.0025 & 0.0869 & 0.9500 \\ 
  IRS-Model & Random & Normal & 0 & 200 & -0.0024 & 0.0872 & 0.9505 \\ 
  GRTS-Design & Random & Normal & 0 & 200 & 0.0027 & 0.0875 & 0.9470 \\ 
  GRTS-Model & Random & Normal & 0 & 200 & 0.0027 & 0.0876 & 0.9505 \\ 

@@

IRS-Design & Random & Lognormal & 0 & 200 & 0.0166 & 0.4146 & 0.8975 \\ 
  IRS-Model & Random & Lognormal & 0 & 200 & 0.0074 & 0.4479 & 0.8930 \\ 
  GRTS-Design & Random & Lognormal & 0 & 200 & -0.0044 & 0.4800 & 0.8870 \\ 
  GRTS-Model & Random & Lognormal & 0 & 200 & -0.0063 & 0.4820 & 0.8875 \\ 

@@

IRS-Design & Gridded & Normal & 0.5 & 200 & -0.0003 & 0.0682 & 0.9735 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 200 & -0.0005 & 0.0664 & 0.9435 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 200 & 0.0002 & 0.0661 & 0.9415 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 200 & 0.0001 & 0.0656 & 0.9450 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 200 & -0.0008 & 0.3556 & 0.9379 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 200 & -0.0030 & 0.3540 & 0.9144 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 200 & -0.0001 & 0.3305 & 0.9029 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 200 & -0.0041 & 0.3287 & 0.9049 \\ 

@@

IRS-Design & Random & Normal & 0.5 & 200 & 0.0039 & 0.0771 & 0.9464 \\ 
  IRS-Model & Random & Normal & 0.5 & 200 & 0.0024 & 0.0684 & 0.9489 \\ 
  GRTS-Design & Random & Normal & 0.5 & 200 & -0.0001 & 0.0658 & 0.9374 \\ 
  GRTS-Model & Random & Normal & 0.5 & 200 & -0.0003 & 0.0652 & 0.9444 \\ 

@@

IRS-Design & Random & Lognormal & 0.5 & 200 & 0.0091 & 0.3861 & 0.9164 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 200 & -0.0048 & 0.3783 & 0.9069 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 200 & 0.0012 & 0.4088 & 0.9029 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 200 & -0.0005 & 0.3941 & 0.9029 \\ 

@@

IRS-Design & Gridded & Normal & 0.9 & 200 & 0.0002 & 0.0413 & 0.9965 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 200 & -0.0008 & 0.0356 & 0.9475 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 200 & -0.0004 & 0.0381 & 0.9475 \\ 

>>>>

  \journal{Methods in Ecology and Evolution} % Sets Journal name

@@

  \title{A comparison of design-based and model-based approaches for finite
population spatial data -- Supplementary Material.}
    \author[USEPA]{Michael Dumelle\corref{1}}

    \author[STLAW]{Matt Higham}

    \author[OSU]{Lisa Madsen}

@@

      \address[USEPA]{United States Environmental Protection Agency, 200 SW 35th St,
Corvallis, Oregon, 97333}
    \address[STLAW]{Saint Lawrence University Department of Mathematics, Computer Science,
and Statistics, 23 Romoda Drive, Canton, New York, 13617}
    \address[OSU]{Oregon State University Department of Statistics, 239 Weniger Hall,
Corvallis, Oregon, 97331}
    \address[NOAA]{Marine Mammal Laboratory, Alaska Fisheries Science Center, National
Oceanic and Atmospheric Administration, Seattle, Washington, 98115}
      \cortext[1]{Corresponding Author: Michael Dumelle (Dumelle.Michael@epa.gov)}

@@

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2.} 
\end{table}

@@

\scalebox{0.85}{

@@

IRS-Design & Gridded & Normal & 0 & 50 & -0.0023 & 0.1968 & 0.9440 \\ 
  IRS-Model & Gridded & Normal & 0 & 50 & -0.0029 & 0.1988 & 0.9400 \\ 
  GRTS-Design & Gridded & Normal & 0 & 50 & -0.0011 & 0.1946 & 0.9110 \\ 
  GRTS-Model & Gridded & Normal & 0 & 50 & -0.0006 & 0.1949 & 0.9300 \\ 

@@

}

@@

IRS-Design & Gridded & Lognormal & 0 & 50 & -0.0036 & 0.2007 & 0.9080 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 50 & -0.0094 & 0.2071 & 0.9045 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 50 & -0.0007 & 0.1962 & 0.8690 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 50 & -0.0022 & 0.1969 & 0.8945 \\ 

@@

IRS-Design & Random & Normal & 0 & 50 & 0.0019 & 0.1861 & 0.9505 \\ 
  IRS-Model & Random & Normal & 0 & 50 & 0.0014 & 0.1892 & 0.9445 \\ 
  GRTS-Design & Random & Normal & 0 & 50 & -0.0040 & 0.1955 & 0.9090 \\ 
  GRTS-Model & Random & Normal & 0 & 50 & -0.0040 & 0.1965 & 0.9315 \\ 

@@

IRS-Design & Random & Lognormal & 0 & 50 & 0.0032 & 0.1843 & 0.9205 \\ 
  IRS-Model & Random & Lognormal & 0 & 50 & -0.0039 & 0.1945 & 0.9105 \\ 
  GRTS-Design & Random & Lognormal & 0 & 50 & -0.0056 & 0.1944 & 0.8870 \\ 
  GRTS-Model & Random & Lognormal & 0 & 50 & -0.0078 & 0.1967 & 0.9075 \\ 

@@

IRS-Design & Gridded & Normal & 0.5 & 50 & 0.0025 & 0.1762 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 50 & 0.0007 & 0.1655 & 0.9305 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 50 & 0.0004 & 0.1524 & 0.9115 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 50 & -0.0003 & 0.1499 & 0.9320 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0004 & 0.1863 & 0.9140 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0076 & 0.1834 & 0.9035 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0016 & 0.1612 & 0.8810 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0017 & 0.1606 & 0.8940 \\ 

@@

IRS-Design & Random & Normal & 0.5 & 50 & 0.0037 & 0.1657 & 0.9590 \\ 
  IRS-Model & Random & Normal & 0.5 & 50 & 0.0027 & 0.1546 & 0.9495 \\ 
  GRTS-Design & Random & Normal & 0.5 & 50 & -0.0034 & 0.1511 & 0.9170 \\ 
  GRTS-Model & Random & Normal & 0.5 & 50 & -0.0037 & 0.1504 & 0.9305 \\ 

@@

IRS-Design & Random & Lognormal & 0.5 & 50 & 0.0023 & 0.1637 & 0.9245 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 50 & -0.0055 & 0.1622 & 0.9125 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 50 & -0.0057 & 0.1570 & 0.9000 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 50 & -0.0079 & 0.1567 & 0.9100 \\ 

@@

IRS-Design & Gridded & Normal & 0.9 & 50 & 0.0053 & 0.1579 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 50 & 0.0026 & 0.1165 & 0.9315 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 50 & 0.0013 & 0.1074 & 0.9220 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 50 & -0.0007 & 0.0949 & 0.9430 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1731 & 0.9220 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0020 & 0.1325 & 0.9135 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1183 & 0.9065 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0002 & 0.1090 & 0.9120 \\ 

@@

IRS-Design & Random & Normal & 0.9 & 50 & 0.0062 & 0.1520 & 0.9525 \\ 
  IRS-Model & Random & Normal & 0.9 & 50 & 0.0037 & 0.1074 & 0.9525 \\ 
  GRTS-Design & Random & Normal & 0.9 & 50 & -0.0029 & 0.1038 & 0.9340 \\ 
  GRTS-Model & Random & Normal & 0.9 & 50 & -0.0027 & 0.0940 & 0.9360 \\ 

@@

IRS-Design & Random & Lognormal & 0.9 & 50 & 0.0053 & 0.1542 & 0.9325 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 50 & -0.0012 & 0.1160 & 0.9115 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 50 & -0.0033 & 0.1150 & 0.9160 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 50 & -0.0031 & 0.1014 & 0.9235 \\ 

@@

IRS-Design & Gridded & Normal & 0 & 100 & -0.0029 & 0.1322 & 0.9430 \\ 
  IRS-Model & Gridded & Normal & 0 & 100 & -0.0033 & 0.1332 & 0.9410 \\ 
  GRTS-Design & Gridded & Normal & 0 & 100 & 0.0041 & 0.1302 & 0.9245 \\ 
  GRTS-Model & Gridded & Normal & 0 & 100 & 0.0038 & 0.1304 & 0.9420 \\ 

@@

IRS-Design & Gridded & Lognormal & 0 & 100 & -0.0052 & 0.1334 & 0.9335 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 100 & -0.0072 & 0.1350 & 0.9300 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 100 & 0.0042 & 0.1303 & 0.9035 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 100 & 0.0034 & 0.1307 & 0.9265 \\ 

@@

IRS-Design & Random & Normal & 0 & 100 & -0.0066 & 0.1366 & 0.9405 \\ 
  IRS-Model & Random & Normal & 0 & 100 & -0.0067 & 0.1370 & 0.9385 \\ 
  GRTS-Design & Random & Normal & 0 & 100 & 0.0028 & 0.1364 & 0.9180 \\ 
  GRTS-Model & Random & Normal & 0 & 100 & 0.0029 & 0.1363 & 0.9345 \\ 

@@

IRS-Design & Random & Lognormal & 0 & 100 & -0.0051 & 0.1348 & 0.9280 \\ 
  IRS-Model & Random & Lognormal & 0 & 100 & -0.0075 & 0.1372 & 0.9230 \\ 
  GRTS-Design & Random & Lognormal & 0 & 100 & 0.0002 & 0.1375 & 0.8840 \\ 
  GRTS-Model & Random & Lognormal & 0 & 100 & -0.0003 & 0.1377 & 0.9090 \\ 

@@

IRS-Design & Gridded & Normal & 0.5 & 100 & -0.0016 & 0.1177 & 0.9540 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 100 & -0.0023 & 0.1072 & 0.9470 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 100 & 0.0051 & 0.0998 & 0.9300 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 100 & 0.0039 & 0.0982 & 0.9470 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 100 & -0.0021 & 0.1211 & 0.9445 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 100 & -0.0058 & 0.1153 & 0.9295 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 100 & 0.0041 & 0.1090 & 0.9085 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 100 & 0.0019 & 0.1090 & 0.9180 \\ 

@@

IRS-Design & Random & Normal & 0.5 & 100 & -0.0064 & 0.1222 & 0.9440 \\ 
  IRS-Model & Random & Normal & 0.5 & 100 & -0.0049 & 0.1073 & 0.9440 \\ 
  GRTS-Design & Random & Normal & 0.5 & 100 & 0.0013 & 0.1041 & 0.9155 \\ 
  GRTS-Model & Random & Normal & 0.5 & 100 & 0.0014 & 0.1020 & 0.9400 \\ 

@@

IRS-Design & Random & Lognormal & 0.5 & 100 & -0.0063 & 0.1204 & 0.9355 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 100 & -0.0097 & 0.1150 & 0.9275 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 100 & 0.0003 & 0.1092 & 0.8960 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 100 & -0.0004 & 0.1088 & 0.9120 \\ 

@@

IRS-Design & Gridded & Normal & 0.9 & 100 & -0.0007 & 0.1059 & 0.9605 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 100 & -0.0019 & 0.0700 & 0.9445 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 100 & 0.0044 & 0.0655 & 0.9435 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 100 & 0.0030 & 0.0585 & 0.9440 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 100 & -0.0011 & 0.1092 & 0.9540 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 100 & -0.0033 & 0.0779 & 0.9330 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 100 & 0.0035 & 0.0757 & 0.9190 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 100 & 0.0017 & 0.0693 & 0.9190 \\ 

@@

IRS-Design & Random & Normal & 0.9 & 100 & -0.0048 & 0.1095 & 0.9430 \\ 
  IRS-Model & Random & Normal & 0.9 & 100 & -0.0017 & 0.0671 & 0.9535 \\ 
  GRTS-Design & Random & Normal & 0.9 & 100 & -0.0009 & 0.0674 & 0.9265 \\ 
  GRTS-Model & Random & Normal & 0.9 & 100 & 0.0000 & 0.0595 & 0.9420 \\ 

@@

IRS-Design & Random & Lognormal & 0.9 & 100 & -0.0045 & 0.1110 & 0.9375 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 100 & -0.0052 & 0.0771 & 0.9310 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 100 & -0.0009 & 0.0732 & 0.9195 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 100 & -0.0007 & 0.0661 & 0.9165 \\ 

@@

IRS-Design & Gridded & Normal & 0 & 200 & 0.0013 & 0.0882 & 0.9550 \\ 
  IRS-Model & Gridded & Normal & 0 & 200 & 0.0013 & 0.0886 & 0.9530 \\ 
  GRTS-Design & Gridded & Normal & 0 & 200 & -0.0045 & 0.0885 & 0.9380 \\ 
  GRTS-Model & Gridded & Normal & 0 & 200 & -0.0045 & 0.0885 & 0.9460 \\ 

@@

IRS-Design & Gridded & Lognormal & 0 & 200 & 0.0001 & 0.0880 & 0.9350 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 200 & -0.0002 & 0.0883 & 0.9355 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 200 & -0.0034 & 0.0898 & 0.9285 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 200 & -0.0035 & 0.0900 & 0.9335 \\ 

@@

IRS-Design & Random & Normal & 0 & 200 & -0.0014 & 0.0893 & 0.9465 \\ 
  IRS-Model & Random & Normal & 0 & 200 & -0.0015 & 0.0896 & 0.9465 \\ 
  GRTS-Design & Random & Normal & 0 & 200 & 0.0007 & 0.0868 & 0.9460 \\ 
  GRTS-Model & Random & Normal & 0 & 200 & 0.0007 & 0.0867 & 0.9490 \\ 

@@

IRS-Design & Random & Lognormal & 0 & 200 & -0.0028 & 0.0891 & 0.9425 \\ 
  IRS-Model & Random & Lognormal & 0 & 200 & -0.0033 & 0.0896 & 0.9395 \\ 
  GRTS-Design & Random & Lognormal & 0 & 200 & 0.0015 & 0.0860 & 0.9365 \\ 
  GRTS-Model & Random & Lognormal & 0 & 200 & 0.0012 & 0.0861 & 0.9415 \\ 

@@

IRS-Design & Gridded & Normal & 0.5 & 200 & 0.0022 & 0.0788 & 0.9535 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 200 & 0.0008 & 0.0678 & 0.9580 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 200 & -0.0024 & 0.0671 & 0.9335 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 200 & -0.0030 & 0.0661 & 0.9410 \\ 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 200 & 0.0016 & 0.0816 & 0.9420 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 200 & -0.0000 & 0.0739 & 0.9335 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 200 & -0.0033 & 0.0744 & 0.9330 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 200 & -0.0041 & 0.0742 & 0.9350 \\ 

@@

IRS-Design & Random & Normal & 0.5 & 200 & -0.0016 & 0.0790 & 0.9480 \\ 
  IRS-Model & Random & Normal & 0.5 & 200 & -0.0010 & 0.0690 & 0.9475 \\ 
  GRTS-Design & Random & Normal & 0.5 & 200 & -0.0002 & 0.0652 & 0.9455 \\ 
  GRTS-Model & Random & Normal & 0.5 & 200 & 0.0001 & 0.0640 & 0.9500 \\ 

@@

IRS-Design & Random & Lognormal & 0.5 & 200 & -0.0027 & 0.0809 & 0.9494 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 200 & -0.0037 & 0.0732 & 0.9454 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 200 & -0.0008 & 0.0671 & 0.9434 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 200 & -0.0012 & 0.0662 & 0.9479 \\ 

@@

IRS-Design & Gridded & Normal & 0.9 & 200 & 0.0021 & 0.0704 & 0.9570 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 200 & 0.0005 & 0.0411 & 0.9590 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 200 & -0.0005 & 0.0423 & 0.9370 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 200 & -0.0012 & 0.0377 & 0.9450 \\ 
